---
title: "linear model from Web"
author: "Marcia Sanchez"
date: "Semester 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```



## Model 1 SIM~ARMS



### scatterplot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
basicNN + geom_point()
```


A scatter plot was created with a positive linear. 

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

We got 1 answer in the result with [1] 0.686. It tell us that there is an amount of  correlation between SIMS and ARM. 

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

We have some important statistics. We have multiple R square and Residual standard Error for SIMS VS. ARM. We have adjusted R square of 467 and multiple r square are 0.4706. As you put more things into the model the result is lower. 


#### Predict at target point



#### scatterplot with model fit
  

## Model 2 SIM~GRIP



### Now add in scatterplot



### Numerical results 



### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

